From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-28 paper.tex
Updated result discussion following use of Cohen kappa

\begin{figure*}[ht!]
    \centering
    \includegraphics[width=\linewidth]{matches-excerpt}
    \caption{\small \textbf{Comparison of computed focus of attention \vs ground
        truth} during a face-to-face child-robot interaction (subject 4
        in table~\ref{tab:results}, 3.5min-long excerpt).
        In blue (top line), the focus of attention as computed by the robot;
        in orange (bottom line), the focus of attention as manually annotated
        (ground-truth). The bottom graph shows agreement between both (whenever
        the head is detected).}

@@

In terms of attention tracking, two groups of children stand out of
Table~\ref{tab:results}: the robot's estimate of the focus of attention for
subjects 1, 4 and 5 has questionable agreement with the ground-truth (Cronbach's
$\alpha$ close to 0.6), while for subjects 2, 3 and 6, we find a good agreement
($\alpha$ close to 0.8). After further analysis of the videos, it
reflects that the first group of children rely more on their eyes to direct
their gaze than the second group. Note that, notwithstanding the small sample
size, it is rather intriguing that the two groups appear so well distinct.
This calls for further experimental investigation.

>>>>

\begin{figure*}[ht!]
    \centering
    \includegraphics[width=\linewidth]{matches-excerpt}
    \caption{\small \textbf{Comparison of computed focus of attention \vs ground
        truth} during a face-to-face child-robot interaction (subject 4
        in table~\ref{tab:results}, 3.5min-long excerpt).
        In blue (top lines), the focus of attention as computed by the robot;
        in orange (bottom lines), the focus of attention as manually annotated
        (ground-truth). Periods where the head is lost are marked with dashed
        vertical lines. The bottom graph shows agreement between both (whenever
        the head is detected).}

@@

In terms of attention tracking, Cohen's $\kappa$ values are between 0.47 and
0.68 with one subject resulting in significantly worst tracking, at 0.26. While
the interpretation of Cohen's $\kappa$ is subject to discussions (the number of
the coded values -- in our case 6 -- and the distribution probability of values
-- in our case, values are \emph{not} equiprobable -- are factors impacting
$\kappa$ independently of the level of agreement), the levels of agreement are
\emph{moderate} to \emph{substantial}, with one subject only
showing \emph{fair} agreement~\cite{landis1977measurement}. Further analysis of
the videos shows that the child with the lowest level of agreement is especially
calm and would rely more on the eyes to direct his gaze than the other children,
thus leading to a less accurate estimation of its focus of attention.
